NLP and NER

### 2021-10-13 NER_analysis_final.Rmd
Cleaning up code

```{r message=FALSE}
radar_facet_sentiment <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(kind == "person") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(10)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

sentiment_Dick_Diver <- entities_matches_sentiment %>% filter(title == "Tender is the Night") %>%
  #Change filter to locations for locations
  filter(words == "Dick") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Gatsby <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(words == "Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% filter(title == "The Great Gatsby") %>% select(-positive, -negative, -sentiment, -kind)

tggp <- the_great_gatsby_protagonist %>% filter(title == "The Great Gatsby") %>% summarise(across(anger:trust, sum))

data_for_gatsby <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, c("Gats", "Jay")), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

new_gatsby <- data_for_gatsby[c(1:3),c(3:10)] %>%  summarise(across(anger:trust, sum)) %>% mutate(protagonist = "Gatsby", .before  = anger)
new_gatsby_sum <- bind_rows(data_for_gatsby, new_gatsby)

data_for_diver <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Dick"), ] %>% filter(title == "Tender is the Night") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

data_for_gatsby <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Gats"), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_daisy <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Dais"), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_gatsby_2 <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Jay"), ] %>% filter(title == "The Great Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

all_protag <- bind_rows(sentiment_Gatsby, sentiment_Anthony, sentiment_Amory, sentiment_Dick_Diver) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

temp_table1 <-bind_rows(data_for_gatsby, data_for_gatsby_2) %>% ungroup() %>% select(-title, -words)
temp_table2 <- data_for_diver %>% ungroup() %>% select(-title, -words)
temp_table3 <- data_for_anthony %>% ungroup() %>% select(-title, -words)
temp_table4 <- data_for_amory %>% ungroup() %>% select(-title, -words)
temp_table5 <- data_for_daisy %>% ungroup() %>% select(-title, -words)
temp_table6 <- data_for_henry %>% ungroup() %>% select(-title, -words)
#sum_anger <- data_for_gatsby %>% sum(anger)
data_for_gatsby_final <- mapply(sum, temp_table1)
data_for_diver_final <- mapply(sum, temp_table2)
data_for_anthony_final <- mapply(sum, temp_table3)
data_for_amory_final <- mapply(sum, temp_table4)
data_for_daisy_final <- mapply(sum, temp_table5)
data_for_henry_final <- mapply(sum, temp_table6)

protag_fitz <- read_csv("protag_f.csv") %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))
Gatsby_scale <- protag_fitz %>% filter(protagonist == "Gatsby")

radar_facet_sentiment_2 <- bind_rows(tender_is_the_night_protagonist, the_great_gatsby_protagonist)

ggRadar(
  # Add select(-total)
  data = all_protag %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

```{r graphs_hemingway}
sentiment_Henry <- entities_matches_sentiment %>% filter(title == "A Farewell to Arms") %>%
  #Change filter to locations for locations
  filter(words == "Henry") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Robert <- entities_matches_sentiment %>% filter(title == "For Whom The Bell Tolls") %>%
  #Change filter to locations for locations
  filter(words == "Robert Jordan") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Jake <- entities_matches_sentiment %>% filter(title == "The Sun Also Rises") %>%
  #Change filter to locations for locations
  filter(words == "Barnes") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_David <- entities_matches_sentiment %>% filter(title == "The Garden of Eden") %>%
  #Change filter to locations for locations
  filter(words == "David") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

all_protag_h <- bind_rows(sentiment_Henry, sentiment_Robert, sentiment_Jake, sentiment_David) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

ggRadar(
  # Add select(-total)
  data = all_protag_h %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)

>>>>

```{r message=FALSE graphs_fitzgerald}
radar_facet_sentiment <- entities_matches_sentiment %>%

  filter(kind == "person") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(10)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

sentiment_Dick_Diver <- entities_matches_sentiment %>% filter(title == "Tender is the Night") %>%
  filter(words == "Dick") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Gatsby <- entities_matches_sentiment %>%
  filter(words == "Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% filter(title == "The Great Gatsby") %>% select(-positive, -negative, -sentiment, -kind)

@@

@@

all_protag_fitz <- bind_rows(sentiment_Gatsby, sentiment_Anthony, sentiment_Amory, sentiment_Dick_Diver) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

ggRadar(

  data = all_protag_fitz %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

```{r graphs_hemingway}
sentiment_Henry <- entities_matches_sentiment %>% filter(title == "A Farewell to Arms") %>%
  filter(words == "Henry") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Robert <- entities_matches_sentiment %>% filter(title == "For Whom The Bell Tolls") %>%
  filter(words == "Robert Jordan") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Jake <- entities_matches_sentiment %>% filter(title == "The Sun Also Rises") %>%
  filter(words == "Barnes") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_David <- entities_matches_sentiment %>% filter(title == "The Garden of Eden") %>%
  filter(words == "David") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

all_protag_hemi <- bind_rows(sentiment_Henry, sentiment_Robert, sentiment_Jake, sentiment_David) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

ggRadar(

  data = all_protag_hemi %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
